Fourmile Calibrations

### 2022-12-03 calibration_output.Rmd
grid 2012  now included
added in all streamflow (sim and obs). need to write function to compute all KGEs and pbias

# KGE

@@

# Parameters

@@

plot_params <- function(param_name) {
  params %>%
    filter(param == param_name) %>%
    ggplot(aes(x = year_missing,
               y = value,
               shape = input_data, 
               color = input_data)) + 
    geom_point(size = 3) + 
    ggtitle(param_name) +
    theme_bw()
}

@@

@@

>>>>

## KGE for calibrations

@@

## Parameters

@@

#function to plot all params
plot_params <- function(param_name) {
  params %>%
    filter(param == param_name) %>%
    ggplot(aes(x = year_missing,
               y = value,
               shape = input_data, 
               color = input_data)) + 
    geom_point(size = 3) + 
    ggtitle(param_name) +
    theme_bw()
}

@@

write.csv(params, 'params.csv')

@@

## Hydrographs

```{r}

flow <- read_csv('discharge_all.csv') %>%
  replace(.==-9999, NA)

flow_pivot <- flow %>%
  pivot_longer(!date, names_to = 'cal_run', values_to = 'q_m3s')

q <- ggplot(flow_pivot, aes(date, q_m3s, color = cal_run)) +
  geom_line()

ggplotly(q)

library(hydroGOF)

KGE(flow$grid_all, flow$obs)
KGE(flow$statn_all, flow$obs)

get_kge <- function() {

}
